\plaintitle

### 2016-08-26 drafts/labor/cases.tex
thursday edits and wb feedback

\subsection{What are the limits of crowdsourcing?}
Research in crowdsourcing has spent the better part of a decade
exploring how to grow the limits of crowdsourcing and
find the boundaries of crowd work and microtasks;
this has largely involved
  identifying challenges to this form of labor,
  overcoming them through novel designs of work--flows and processes, and
  repeating the process
\cite{bernsteinSoylent}.
The question that has emerged
among these researchers and
through the work that they have produced then
has been driving at \textit{whether} there are limits to crowdsourcing
(and, if so, what factors determine those limits).
Through this lens, we can point to
a number of contributions to the field that have extended the boundaries of crowd work.

>>>>

We look at lots of papers that use the term ``crowdsourcing'' or ``crowdwork''
in the abstracts and titles of their papers,
especially the papers that we cited earlier, to try
to answer the questions that we posed in the introduction.
Then we look to the piecework literature to see whether and to what extent
piecework answers the questions we, crowdsourcing researchers, have asked.
We then see whether and how crowdsourcing as we know it has differed from piecework,
and how that affects the predictions and conclusions made in the piecework literature.
% look at review papers

% what's the methodology?
% make piecework literature much clearer about argument
% make headers clearer to signal what i'm doing here.

\subsection{What are the limits of crowdsourcing?}
\topic{Research in crowdsourcing has spent the better part of a decade
exploring how to grow the limits of crowdsourcing and
find the boundaries of crowd work and microtasks.}
This has largely involved
  identifying challenges to this form of labor,
  overcoming them through novel designs of work--flows and processes, and
  repeating the process
\cite[e.g.][]{bernsteinSoylent,foundry,crowdForgeKittur}.
The question that has emerged
among these researchers and
through the work that they have produced then
has been driving at \textit{whether} there are limits to crowdsourcing
(and, if so, what factors determine those limits).
Through this lens, we can point to
a number of contributions to the field that have extended the boundaries of crowd work.

### 2016-08-26 drafts/labor/complexity.tex
thursday edits and wb feedback

\subsubsection{Achieving greater complexity
\joke{ --- or ``making crowd--work \textit{yuge}''}
% i think it says a lot about my confidence in my latex skillz that i'm willing to put these in the subfile
}\label{sec:Complexity}

\topic{Crowdsourcing research has spent the better part of a decade attempting
to prove the viability of crowdsourcing in increasingly complex work.}  % this is my topic sentence.
\citeauthor{crowdForgeKittur}
map the discussion toward this goal in their work on
crowdsourcing complex work
\cite{crowdForgeKittur}.
The broader body of work has varied significantly in type
--- providing conversational assistants,
interpreting medical data, and
telling coherent and compelling stories,
to name a few examples
\cite{Lasecki:2013:CCC:2501988.2502057,mavandadi2012distributed,KimStoria}.

\topic{This body of research has involved similar approaches to problems,
often involving insights made in Computer Science and applied to human work--flows.}
The crowdwork literature typically identifies target milestones in CS
that have presented significant challenges for researchers,
leverages some of the approaches and insights that Computer Science researchers have already made
(for example, MapReduce in the case of \citeauthor{crowdForgeKittur}'s \textit{CrowdForge}),
and arranges humans as computational black boxes within those approaches and processes
\cite[][and others]{crowdForgeKittur,foundry}.

\topic{This approach has proven a compelling one because
it leverages the in--built advantages that technology and digital media afford.}
\textit{Foundry}'s tools for managing and arranging expert groups into a cohort
allow researchers to convincingly argue that expert teams can be rapidly formed,
just like non--expert teams
\cite{foundry}.

\topic{The research into piecework has identified a number of
major constraints that we should expect to find when
applying piecework approaches to work.}
\citeauthor{10.2307/23702539},
who describes piecework as
    ``\dots~based on examination of various shop jobs,
    which included calculation of the standard time and compensation for each task''
\cite{10.2307/23702539}.
\citeauthor{10.2307/23702539} later enumerates some of the roles required
to facilitate piecework in the early \nth{20} century:
    ``\dots~piecework clerks, inspectors, and ``experts''\dots''
\cite{10.2307/23702539}.
\citeauthor{Brown01041990} makes a more assertive
claim about the factors necessary for piecework to thrive,
specifically arguing that
    ``\dots~incentive pay is less likely in jobs with
    a variety of duties than in jobs with a narrow set of routinized duties''
\cite{Brown01041990}.
\citeauthor{10.2307/23702539} makes another claim that
successful cases of piecework owed themselves in part to the fact that
    ``\dots~only [the largest and most wealthy railroads] had the resources to~\dots
    pay the overhead involved in installing work reorganization''
\cite{10.2307/23702539}.

>>>>

\subsubsection{Achieving greater complexity
\joke{ --- or ``making crowd--work \textit{yuge}''}
% i think it says a lot about my confidence in my latex skillz that i'm willing to put these in the subfile
}\label{sec:Complexity}
% crowd weaver, aditya and someone else's book
\topic{Crowdsourcing research has spent the better part of a decade attempting
to prove the viability of crowdsourcing in increasingly complex work.}  % this is my topic sentence.
\citeauthor{crowdForgeKittur}
map the discussion toward this goal in their work on
crowdsourcing complex work
\cite{crowdForgeKittur}.
The broader body of work has varied significantly in type
--- providing conversational assistants,
interpreting medical data, and
telling coherent and compelling stories,
to name a few examples
\cite{Lasecki:2013:CCC:2501988.2502057,mavandadi2012distributed,KimStoria}.

\topic{This body of research has involved similar approaches to problems,
often involving insights made in Computer Science and applied to human work--flows.}
The crowdwork literature typically identifies target milestones in CS
that have presented significant challenges for researchers,
leverages some of the approaches and insights that Computer Science researchers have already made
(for example, MapReduce in the case of \citeauthor{crowdForgeKittur}'s \textit{CrowdForge}),
and arranges humans as computational black boxes within those approaches and processes
\cite[][and others]{crowdForgeKittur,foundry}.
This approach has proven a compelling one because
it leverages the in--built advantages that technology and digital media afford.
\textit{Foundry}'s tools for managing and arranging expert groups into a cohort
allow researchers to convincingly argue that expert teams can be rapidly formed,
just like non--expert teams
\cite{foundry}.

\topic{The research into piecework makes the case that
piecework has been limited principally by the challenges of human management and oversight.}
\citeauthor{10.2307/23702539},
who describes piecework as
    ``\dots~based on examination of various shop jobs,
    which included calculation of the standard time and compensation for each task'',
argues that piecework must be rigorously evaluated at a time that demands
\textit{other people} perform the evaluation.
% \cite{10.2307/23702539}.
\citeauthor{10.2307/23702539} later enumerates some of the roles required
to facilitate piecework in the early \nth{20} century:
    ``\dots~piecework clerks, inspectors, and ``experts''\dots''
\cite{10.2307/23702539}.
This criterion strictly limits the extent to which piecework can grow in complexity;
it must, for instance, be quickly evaluable by another person.

\topic{Piecework researchers also make claims regarding
the organizations that benefit from piecework in the first place.}
\citeauthor{Brown01041990} discusses the factors necessary for piecework to thrive:
    ``\dots~incentive pay is less likely in jobs with
    a variety of duties than in jobs with a narrow set of routinized duties''
\cite{Brown01041990}.
\citeauthor{10.2307/23702539} adds further, that
successful cases of piecework owed themselves in part to the fact that
    ``\dots~only [the largest and most wealthy railroads] had the resources to~\dots
    pay the overhead involved in installing work reorganization''
\cite{10.2307/23702539}.
Together, \citeauthor{10.2307/23702539} and \citeauthor{Brown01041990}
make a persuasive argument that piecework is limited in complexity by
managerial overhead and the fixed cost of adopting a piecework payment regime.

### 2016-08-26 drafts/labor/introduction.tex
moving things around
thursday edits and wb feedback

\section{Introduction}
The past decade has seen a flourishing of on--demand work
where the statuses of workers have become so fleeting that 
these workers
(known colloquially as ``Turkers'')
have been described as ``transient''
\cite{kargerIterativeLearning,mitraComparingStrategies,latozaCrowdDev}.
The realization
that tasks can be accomplished by directing and managing this crowd of workers
has spurred the research and and industry communities to flock to sites of labor
like Amazon's Mechanical Turk (AMT)
to explore the limits of this distributed, seemingly ephemeral labor force.
Researchers in particular have taken to the space in earnest,
finding opportunities to enable new forms of work
as well as using Turkers
as representative populations of the public
\cite{bernsteinSoylent,redballoon,paolacci2010running}.

@@

Indeed, this on--demand workforce has sparked interest
across industries ranging
livery (driving for hire, for example Uber),
house--cleaning (Handy),
and generalized services (TaskRabbit)
\cite{uberOfficial,zaarlyOfficial,taskrabbitOfficial}.
Today, a rapidly growing transient workforce is forming,
itself assembling piece--by--piece as industries and researchers find yet more unexpected ways
to benefit from a latent pool of previously vetted workers
\cite{pewSharing}.

@@

The extant body of work has ostensibly sought to answer one underlying question:
What does the future hold for work and those that do it? % expand on ...?
Researchers have offered their input on this open question along three major threads of scholarship:
\begin{enumerate}
  \item What are the limits of crowdsourcing?
  Perhaps more tightly constrained,
  what can and cannot be done by crowd workers?
    \cite{foundry,suzukiAtelier,KimStoria,yuanAlmost,YuEncouragingOutside,embracingErrorKrishna,Nebeling:2016:WCW:2858036.2858169,Hahn:2016:KAB:2858036.2858364};
  \item What forms of work design, and worker management and arrangement, are viable?
    \cite{bernsteinSoylent,sensitiveTasks,LykourentzouPersonalityMatters,KucherbaevReLauncher,Law:2016:CKC:2858036.2858144,Cai:2016:CRI:2858036.2858237,Chang:2016:ACC:2858036.2858411,Newell:2016:OMA:2858036.2858490}; and%
  \item What will work and the place of work look like for the workers?
    \cite{turkopticon,storiesIraniSilberman,dynamo,crowdcollab,whyWouldAnyoneBrewer,takingAHITMcInnis}
\end{enumerate}

@@

We offer a framing for crowd work spanning the aforementioned industries
collectively as a contemporary instantiation of ``piecework''.
Piecework as a metaphor for the type of work at hand is not new.
Indeed,
\citeauthor{crowdworkFuture} in \citeauthor{crowdworkFuture}
referenced crowd work as ``piecework'' briefly
as a loose analogy to the form of work emerging at the time
\cite{crowdworkFuture}.

But more than this,
the framing of on--demand labor as piecework (re--instantiated)
allows us to attempt to make sense of the broader research on this new form of work
by evaluating this work through a much more refined lens.
More concretely, by looking at task--based or ``gig'' work as
an instantiation (or even a continuation) of piecework,
and by looking for patterns of behavior that the corresponding literature predicts
on this basis, we can
\begin{inlinelist}
  \item make sense of the phenomena so far as part of a much larger series of interrelated events;
  \item bring into focus the ongoing work among workers, system--designers, and researchers in this space; and finally,
  \item offer predictions of what social computing researchers,
        and workers themselves,
        should expect to see on the horizon of on--demand work.
\end{inlinelist}

We'll look at a broad range of cases under a number of major themes
we propose as broadly describing the types of research being done in crowd work
and more generally in what we argue is contemporary piecework.
After validating this lens as a way of reasoning about on--demand labor,
we'll attempt to use this perspective to suggest areas of research worth anticipating,
and developments we should expect to see in the maturation of digitally mediated work.
Finally, we will offer design implications based on this research\dots

\endnote{
\textbf{notes/what i want to get across\dots}

\begin{itemize}
  \item on--demand labor has consumed an increasing proportion of the labor market in the past ten years [\textit{Pew research on on--demand labor}];
  the work  has ranged from Turk work processes
  \item some of it has been about resisting Uber \& other gig labor platforms \cite{bernsteinSoylent,uberAlgorithm};
  some researchers have tackled understanding this new instantiation of work, but come up short (\textit{how}).

@@

  \item this paper will trace the body of research describing microwork --- and later gig work --- and place it in the context of historical piecework and the industrial revolution as a whole.
  \item informed by this new lens, we'll then turn our attention to the future of this re--emergent form of work, and suggest ways that researchers and users of on--demand labor might influence the outcomes we predict in this paper.
\end{itemize}
\upshape}

\onlyinsubfile{
  \balance{}
  \printbibliography
  \theendnotes
}

>>>>

% what am i trying to say? that crowd work is an instantiation of piecework
% framing/bullet points

\section{Introduction}
\topic{The past decade has seen a flourishing of on--demand work,
motivated by the framing of work as
contextually abstract and therefore
interchangeable and modular.}
The statuses of many of these workers
(known colloquially as ``Turkers'')
have become so fleeting that 
they have been described as ``transient''
\cite{kargerIterativeLearning,mitraComparingStrategies,latozaCrowdDev}.
The realization
that tasks can be accomplished by directing and managing this crowd of workers
has spurred the research and and industry communities to flock to sites of labor
like Amazon's Mechanical Turk (AMT)
to explore the limits of this distributed, seemingly ephemeral labor force.
Researchers in particular have taken to the space in earnest,
finding opportunities to enable new forms of work
as well as using Turkers
as representative populations of the public
\cite{bernsteinSoylent,redballoon,paolacci2010running}.

@@

\topic{This matters because\dots}
Indeed, this on--demand workforce has sparked interest
across industries ranging
driving for hire (for example Uber),
house--cleaning (Handy),
and generalized services (TaskRabbit)
\cite{uberOfficial,zaarlyOfficial,taskrabbitOfficial}.
Today, a rapidly growing transient workforce is forming,
itself assembling piece--by--piece as industries and researchers find yet more unexpected ways
to benefit from a latent pool of previously vetted workers
\cite{pewSharing}.

@@

The extant body of work has ostensibly sought to answer one underlying question:
What does the future hold for work and those that do it? % expand on ...?
Researchers have offered their input on this open question along three major threads of scholarship:
\begin{enumerate}
  \item What are the limits of crowdsourcing?
  Perhaps more tightly constrained,
  what can and cannot be done by crowd workers?
    \cite{foundry,suzukiAtelier,KimStoria,yuanAlmost,YuEncouragingOutside,embracingErrorKrishna,
          Nebeling:2016:WCW:2858036.2858169,Hahn:2016:KAB:2858036.2858364};
  \item What forms of work design, and worker management and arrangement, are viable?
    \cite{bernsteinSoylent,sensitiveTasks,LykourentzouPersonalityMatters,KucherbaevReLauncher,
          Law:2016:CKC:2858036.2858144,Cai:2016:CRI:2858036.2858237,
          Chang:2016:ACC:2858036.2858411,Newell:2016:OMA:2858036.2858490}; and%
  \item What will work and the place of work look like for the workers?
    \cite{turkopticon,storiesIraniSilberman,dynamo,crowdcollab,whyWouldAnyoneBrewer,
          takingAHITMcInnis}
\end{enumerate}

@@

We offer a framing for crowd work spanning the aforementioned industries
collectively as a contemporary instantiation of ``piecework''.
Piecework as a metaphor for the type of work at hand is not new.
Indeed,
\citeauthor{crowdworkFuture} in \citeyear{crowdworkFuture}
referenced crowd work as ``piecework'' briefly
as a loose analogy to the form of work emerging at the time
\cite{crowdworkFuture}.
But more than this,
the framing of on--demand labor as a re--instantiation of piecework
gives us more material to make sense of the broader research on this new form of work
by evaluating this work through a much more refined theoretical lens,
informed by decades of rigorous, empirically based research.

More concretely, by looking at task--based or ``gig'' work as
an instantiation (or even a continuation) of piecework,
and by looking for patterns of behavior that the corresponding literature predicts
on this basis, we can
\begin{inlinelist}
  \item make sense of the phenomena so far as part of a much larger series of interrelated events;
  \item bring into focus the ongoing work among
        workers,
        system--designers, and
        researchers in this space;
        and finally,
  \item offer predictions of what social computing researchers,
        and workers themselves,
        should expect to see on the horizon of on--demand work.
\end{inlinelist}

We'll look at a broad range of cases under a number of major themes
we propose as broadly describing the types of research being done in crowd work
and more generally in what we argue is contemporary piecework.
After validating this lens as a way of reasoning about on--demand labor,
we'll attempt to use this perspective to suggest areas of research worth anticipating,
and developments we should expect to see in the maturation of digitally mediated work.
Finally, we will offer design implications based on this research.

\onlyinsubfile{
  \balance{}
  \printbibliography
  % \theendnotes
\nobalance{}
\clearpage
\begin{appendices}
\section{Sleeping kittens}
\begin{itemize}
  \item on--demand labor has consumed an increasing proportion of the labor market in the past ten years [\textit{Pew research on on--demand labor}];
  the work  has ranged from Turk work processes
  \item some of it has been about resisting Uber \& other gig labor platforms \cite{bernsteinSoylent,uberAlgorithm};
  some researchers have tackled understanding this new instantiation of work, but come up short (\textit{how}).

@@

  \item this paper will trace the body of research describing microwork --- and later gig work --- and place it in the context of historical piecework and the industrial revolution as a whole.
  \item informed by this new lens, we'll then turn our attention to the future of this re--emergent form of work, and suggest ways that researchers and users of on--demand labor might influence the outcomes we predict in this paper.
\end{itemize}
\end{appendices}

}
